---
title: "Intro-to-github-lesson-1"
author: "Brody G"
date: "2024-10-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
source("setup.R")
```

```{r}
data("knz_bison")
view(knz_bison)
```
1. Create a new column in the bison dataset that calculates the individual's age at the time of observation.
```{r}
knz_bison_age_data <- knz_bison %>%
  mutate("Age at time of observation" = rec_year - animal_yob) %>% 
  print(knz_bison_age_data)
```

2.  Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).
```{r}
weight_threshold = 1100

knz_bison_filtered_weight_data <- knz_bison %>%
    filter(animal_weight >= weight_threshold)  # Keep records with weight above the threshold
  
print(knz_bison_filtered_weight_data)

```

3.  Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.

```{r}
ggplot(knz_bison, aes(x = animal_sex, y = animal_weight, fill = animal_sex)) +
  geom_boxplot() +
  labs(title = "Weight Distribution by Sex",
       x = "Animal Sex",
       y = "Animal Weight") +
  theme_bw()

t.test(animal_weight ~ animal_sex, data = knz_bison)
```


