---
title: "Pull_Request_Exercise_with_Kenya_Climate_Data"
author: "Brody G"
date: "2024-10-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("setup.R")
```

```{r}
library(tidyverse)
```

```{r}
read_csv('kenya_county_climates.csv')

Kenya_percipitation_data <-read_csv('kenya_county_climates.csv')

print(Kenya_percipitation_data)
```

1.  `select()` just the columns that have "Precipitation" in the name (so we are only interested in the precipitation data), AND the 'County' column.

```{r}
Kenya_data_percipitaiton_to_county_only <- Kenya_percipitation_data %>%
  select(County, contains("Precipitation"))

print(Kenya_data_percipitaiton_to_county_only)

#Other worse way to do it that I did first below  -->
#select(Kenya_percipitation_data, Precipitation_585_30, Precipitation_585_50, Precipitation_585_70, Precipitation_585_90, #Precipitation_hist, County)
```



2.  `filter()` all the rows where 'Precipitation_585_90' is **greater than** the mean precipitation for all counties.

```{r}
Kenya_Percipitation_Mean <- mean(Kenya_data_percipitaiton_to_county_only$Precipitation_585_90, na.rm = TRUE)

Kenya_Percipitation_Data_Filtered <- Kenya_data_percipitaiton_to_county_only %>%
  filter(Precipitation_585_90 > Kenya_Percipitation_Mean)

#Checking Mean
view(Kenya_Percipitation_Mean)

print(Kenya_Percipitation_Data_Filtered)
```


3.  `pivot_longer()` so we have one column for all precip values and one column with the value's associated variables (while keeping County as its own column too).

```{r}
Final_Kenya_Percipitation_Data <- Kenya_Percipitation_Data_Filtered %>%
  pivot_longer(
    cols = contains ("Precipitation"),
     #Had to fix the names_to / values_to functions
    names_to = "Precipitation_Type",    
    values_to = "Precipitation_History")

print(Final_Kenya_Percipitation_Data)
```

Question: How many counties have predicted precip values greater than the total county average?

```{r}
unique(Final_Kenya_Percipitation_Data$County)

#Answer : 22 Counties 
```


4. Using the new dataset created above, create a bar plot of precipitation for each time frame for each county using `facet_wrap()`

```{r}
  ggplot(Final_Kenya_Percipitation_Data, aes(x = County, y = Precipitation_History, fill = Precipitation_Type)) +
  geom_bar(stat = "identity") + # <-- Had to get help on this one 
  labs(title = "Filtered Precipitation Values by County",
       x = "County",
       y = "Precipitation Value") +
  facet_wrap(~ Precipitation_Type, scales = "free_y") + 
  theme_bw()

#Could Not Figure out the Challenge Sorry :/
```
